---
title: "04_proportions"
output: html_document
---

# Clean env and install packages
```{r setup, include=FALSE}
# packages
library(tidyverse)
library(reshape2)
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
```


# Read in data
```{r}
# clear environment
rm(list = ls())

modality <- c("stream") #, "FA", "AD", "RD", "MD")
headers <- read.table("../../labels/subfield_MTL_labels.txt", header=T, sep="")

for (m in modality){
  temp <- list.files(path=paste0("../../data/connectomes/MTL_hipp_",m), pattern="*.csv",
                     recursive = T, full.names = T)
  for (k in 1:length(temp)) assign(temp[k], read.csv(temp[k], header=F, sep=","))

  temp_data <- list()
  for (i in 1:length(temp)){
    temp_data[[i]] <- mget(temp[i])
    names(temp_data[[i]]) <- temp[i]
  }
  assign(paste0(m,"_data"), temp_data)
}

# tsp <- read.csv("../../data/hipp_paths_edit/tracks_edited_exc.csv", header = F)
# colnames(tsp) <- c("ID", "side", "variable", "value")
# tsp$variable <- gsub("_", "/", tsp$variable)

```

# Get connectome labels
```{r}

# Subjects in a list
sbj_list <- as.list(grep("stream", stream_data))

columns <- c()
for (i in 1:length(headers$Clear.Label)){
  for (t in 1:length(headers$Clear.Label)){
    column_name <- paste(headers$Clear.Label[i], headers$Clear.Label[t], sep="/")
    columns <- append(columns, column_name)
  }
}

```

# Normalize streamline data
```{r}
# stream_mat <- vector()
# for (i in 1:length(stream_data)){
#   stream_mat <- rbind(stream_mat, t(as.vector(
#     as.matrix(stream_data[[i]][[1]])/sum(as.matrix(stream_data[[i]][[1]])))))
# }
```

# Separate Right and Left hemisphere
```{r}
right_coor <- grep("R_", headers$Clear.Label)
left_coor <- grep("L_", headers$Clear.Label)

# Separate R and L labels
R_columns <- c()
for (i in right_coor) {
  for (t in right_coor){
    R_column_name <- paste(headers$Clear.Label[i], headers$Clear.Label[t], sep="/")
    R_columns <- append(R_columns, R_column_name)
  }
}

L_columns <- c()
for (j in left_coor){
  for (k in left_coor){
    L_column_name <- paste(headers$Clear.Label[j], headers$Clear.Label[k], sep="/")
    L_columns <- append(L_columns, L_column_name)
  }
}

```

# Gather all participant data
```{r}
#### Take upper/lower triangular ######
to.upper<-function(X) t(X)[lower.tri(X,diag=FALSE)]

# Right 
for (m in modality){
  R_upper_temp <- data.frame()
  for (i in 1:length(get(paste0(m, "_data")))) {
    person_temp <-
      data.frame(t(to.upper(matrix(unlist(get(paste0(m, "_data"))[i]), 
                                   nrow = length(headers$Clear.Label),
                                   ncol = length(headers$Clear.Label))
                            [right_coor, right_coor])))
    # person_temp$ID <- sub(paste0("../../../data/HCP_connectomes/connect_hipp+MTL_", m, "/sub-"),"",
    #                       (sub(paste0("_MTL_hipp_connectome_", m, ".csv"),"",
    #                            names(get(paste0(m, "_data"))[[i]]))))
    person_temp$ID <- 
      strsplit(names(get(paste0(m, "_data"))[[i]]), "sub-")[[1]][2] %>%
      strsplit("_") %>%
      .[[1]] %>%
      .[[1]]
    
    R_upper_temp <- rbind(R_upper_temp, person_temp)
  }
  R_conn <- matrix(R_columns,
                   nrow = length(headers$Clear.Label[right_coor]),
                   ncol = length(headers$Clear.Label[right_coor]))
  R_upper_columns <- to.upper(R_conn)
  R_upper_columns <- c(R_upper_columns, "ID")
  colnames(R_upper_temp) <- c(R_upper_columns)
  
  assign(paste0("R_data_", m), R_upper_temp)
}

# 
# sub(paste0("_MTL_hipp_connectome_", m, ".csv"), "",names(get(paste0(m, "_data"))[[i]]))
# person_test$ID <- sub("../../data/connect_stream/conn/sub-","",
#                         (sub("_hipp_connectome_stream.csv","",
#                              names(stream_data[[i]]))))
# 

# Left
for (m in modality){
  L_upper_temp <- data.frame()
  for (i in 1:length(get(paste0(m, "_data")))) {
    person_temp <-
      data.frame(t(to.upper(matrix(unlist(get(paste0(m, "_data"))[i]), 
                                   nrow = length(headers$Clear.Label),
                                   ncol = length(headers$Clear.Label))
                            [left_coor, left_coor])))
    # person_temp$ID <- sub(paste0("../../../data/HCP_connectomes/connect_hipp+MTL_", m, "/sub-"),"",
    #                       (sub(paste0("_MTL_hipp_connectome_", m, ".csv"),"",
    #                            names(get(paste0(m, "_data"))[[i]]))))
    person_temp$ID <- 
      strsplit(names(get(paste0(m, "_data"))[[i]]), "sub-")[[1]][2] %>%
      strsplit("_") %>%
      .[[1]] %>%
      .[[1]]
        
    L_upper_temp <- rbind(L_upper_temp, person_temp)
  }
  L_conn <- matrix(L_columns,
                   nrow = length(headers$Clear.Label[left_coor]),
                   ncol = length(headers$Clear.Label[left_coor]))
  L_upper_columns <- to.upper(L_conn)
  L_upper_columns <- c(L_upper_columns, "ID")
  colnames(L_upper_temp) <- c(L_upper_columns)
  
  assign(paste0("L_data_", m), L_upper_temp)
}

```


# TSP 
```{r}

tsp <- read.csv("../../data/hipp_paths_edit/tracks_edited_exc.csv", header = F)
colnames(tsp) <- c("ID", "side", "variable", "value")
tsp$variable <- gsub("_", "/", tsp$variable)

tsp_wide <-
  tsp %>% pivot_wider(names_from = c("side", "variable"))

L_data_stream$`L_CA2CA3/L_CA4DG`<- tsp_wide$`L_CA4DG/CA2CA3`
L_data_stream$`L_CA2CA3/L_CA1` <- tsp_wide$`L_CA2CA3/CA1`
#L_data_stream <- merge(L_data_stream, tsp_wide[,c("ID","L_CA2CA3/CA1","L_CA4DG/CA2CA3")], by = "ID")

R_data_stream$`R_CA2CA3/R_CA4DG` <- tsp_wide$`R_CA4DG/CA2CA3`
R_data_stream$`R_CA2CA3/R_CA1` <- tsp_wide$`R_CA2CA3/CA1`
#R_data_stream <- merge(R_data_stream, tsp_wide[,c("ID","R_CA2CA3/CA1","R_CA4DG/CA2CA3")], by = "ID")

```


# get rid of PRC PHC
```{r}

R_data_stream_new <-
  R_data_stream[-which(grepl("PRC", colnames(R_data_stream)) |
                       grepl("PHC", colnames(R_data_stream)) |
                          grepl("stratum", colnames(R_data_stream)))]

L_data_stream_new <-
  L_data_stream[-which(grepl("PRC", colnames(L_data_stream)) |
                       grepl("PHC", colnames(L_data_stream)) |
                          grepl("stratum", colnames(L_data_stream)))]

data_stream <- merge(R_data_stream_new, L_data_stream_new, by = "ID")
  
#data_stream <-
data_stream <-
  data_stream %>%
  rowwise(ID) %>%
  mutate(total = sum(c_across(`R_subiculum/R_CA1`:`L_ERC/L_CA2CA3`))/2) #### HERE!!!
  #  rowwise() %>%
  #   mutate(tot = summarise(across(2:20, mean)))
  # as.data.frame()
    #summarise_at(vars("ID"), list(name = mean))
  
data_stream <-
  data_stream %>%
  #group_by("ID") %>%
  rowwise(ID) %>%
  mutate('CA2CA3/CA4DG' = (`R_CA2CA3/R_CA4DG` + `L_CA2CA3/L_CA4DG`)/2,
         'CA2CA3/CA1' = (`R_CA2CA3/R_CA1` + `L_CA2CA3/L_CA1`)/2,
         'subiculum/CA1' = (`R_subiculum/R_CA1` + `L_subiculum/L_CA1`)/2,
         'ERC/subiculum' = (`R_ERC/R_subiculum` + `L_ERC/L_subiculum`)/2,
         'ERC/CA1' = (`R_ERC/R_CA1` + `L_ERC/L_CA1`)/2)
         # 'CA4DG/subiculum' = mean(`R_CA4DG/R_subiculum` + `L_CA4DG/L_subiculum`),

data_stream <-
  data_stream %>%
  #group_by("ID") %>%
  rowwise(ID) %>%
  mutate('CA2CA3/CA4DG_prop' = (`CA2CA3/CA4DG`)*100/total,
         'CA2CA3/CA1_prop' = (`CA2CA3/CA1`)*100/total,
         'subiculum/CA1_prop' = (`subiculum/CA1`)*100/total,
         'ERC/subiculum_prop' = (`ERC/subiculum`)*100/total,
         'ERC/CA1_prop' = (`ERC/CA1`)*100/total)

```


```{r}

data_melt <-
  data_stream %>%
  select(28:32) %>%
  melt()

data_melt$variable <-
  factor(data_melt$variable,
         levels = c("ERC/CA1_prop",
                    #"CA4DG/SUB",
                    "CA2CA3/CA4DG_prop",
                    "CA2CA3/CA1_prop",
                    "subiculum/CA1_prop",
                    "ERC/subiculum_prop"
                    ))

ggplot(data_melt, aes(x=variable, y=value, fill=variable)) +
      #geom_boxplot(aes(y = value))
  geom_violin(aes(y = value))

```


```{r}
# mean(data_stream$total)

# mean(data_stream$total, na.rm = T)

pro_DG_CA3 <- mean(data_stream$`CA2CA3/CA4DG`, na.rm = T)/mean(data_stream$total, na.rm = T)*100
pro_CA3_CA1 <- mean(data_stream$`CA2CA3/CA1`, na.rm = T)/mean(data_stream$total, na.rm = T)*100
pro_ERC_CA1 <- mean(data_stream$`ERC/CA1`, na.rm = T)/mean(data_stream$total, na.rm = T)*100
pro_ERC_SUB <- mean(data_stream$`ERC/subiculum`, na.rm = T)/mean(data_stream$total, na.rm = T)*100
pro_SUB_CA1 <- mean(data_stream$`subiculum/CA1`, na.rm = T)/mean(data_stream$total, na.rm = T)*100

print("pro_DG_CA3")
pro_DG_CA3

print("pro_CA3_CA1")
pro_CA3_CA1

print("pro_ERC_CA1")
pro_ERC_CA1

print("pro_ERC_SUB")
pro_ERC_SUB

print("pro_SUB_CA1")
pro_SUB_CA1

```


# Plot Total Hipp connections
```{r}
 (ggplot(data_stream, aes(x = "Hippocampal circuit", y = total, fill ="Hippocampal circuit")) +
    ggdist::stat_halfeye(
    ## custom bandwidth
    adjust = .5,
    ## adjust height
    width = .6,
    ## move geom to the right
    justification = -.4,
    ## remove slab interval
    .width = 0,
    point_colour = NA,
    #alpha = 0.8,
   # limits = c(10, NA)
    #align = ggdist::align_boundary(at = 10)
   ) +
  geom_boxplot(width = .20,
                   #outlier.shape=8,
                   outlier.size = 0.2,
               #alpha = 0.8,
                   #notch=TRUE,
                   aes(y = total)) + #, fill = side)) +
      # geom_errorbar()+
      # geom_violin(aes(y = value, fill = side)) +
      # geom_dotplot(binaxis= "y",
      #            stackdir = "center",
      #            dotsize = 0.01,
      #            position = "dodge") +
      # scale_x_discrete(#name = "Hemisphere",
      #                 breaks = c("ERC/CA1",
      #                 #"CA4DG/SUB",
      #                 "CA4DG/CA2CA3",
      #                 "CA2CA3/CA1",
      #                 "SUB/CA1",
      #                 "ERC/SUB"),
      #                 labels = c("ERC/CA1",
      #                 #"DG/SUB",
      #                 "DG/CA3",
      #                 "CA3/CA1",
      #                 "SUB/CA1",
      #                 "ERC/SUB"))+
      scale_fill_manual(#name = "Hemisphere",
                      breaks = c("Hippocampal circuit"),
                      values=c("#979797" #"peachpuff4",
                               )) +
                      #labels = c("Right", "Left"))+
      ylab("Streamline density") +
      xlab(" ") +
      #stat_compare_means(aes(group = side), label = "p.signif", paired = TRUE) +
      theme(
        #legend.title = element_text(colour="black", size = 12, face = "bold"),
        axis.text.x=element_text(size=9,color="black", face="bold"),
        axis.text.y=element_text(size=12,color="black"),
        axis.line.y.left =element_line(size=0.5, color = "black"),
        axis.line.x.bottom =element_line(size=0.5, color = "black"),
        axis.title.x = element_text(color="black", size=13, face="bold", vjust=-0.8), # vjust=0.5),
        axis.title.y = element_text(color="black", size=13, face="bold", vjust=1.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white", color = "white"),
        legend.position = "none",
        # legend.background = element_rect(fill = "white", color = "white")
        #plot.background = element_rect(fill = "transparent", color = NA)# vjust=0.5)
        )) %>%
    ggsave(paste0("../../plots/distribution/pathways_violin_whole_hipp_", "stream", ".png"), .,
           width = 2.5, height = 3, dpi = 800 #,
           #bg = "transparent"
           )

```


# TSP connectivity - CA2CA3
```{r}

node_tot <-
  data_stream[2:21][,which(grepl("CA2CA3", colnames(data_stream[2:21])))]
  # mutate(ID = data_stream["ID"])
node_tot$ID <- data_stream$ID

node_tot <-
  node_tot %>%
  rowwise(ID) %>%
  mutate(total = sum(c_across(1:8))/2)

mean((node_tot$`R_CA2CA3/R_CA4DG` + node_tot$`L_CA2CA3/L_CA4DG`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100
mean((node_tot$`R_CA2CA3/R_CA1` + node_tot$`L_CA2CA3/L_CA1`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100


```


# TSP connectivity - CA1
```{r}
node_tot <-
  data_stream[2:21][,which(grepl("CA1", colnames(data_stream[2:21])))]
  # mutate(ID = data_stream["ID"])
node_tot$ID <- data_stream$ID

node_tot <-
  node_tot %>%
  rowwise(ID) %>%
  mutate(total = sum(c_across(1:8))/2)

#mean((node_tot$`R_CA2CA3/R_CA4DG` + node_tot$`L_CA2CA3/L_CA4DG`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100
mean((node_tot$`R_CA2CA3/R_CA1` + node_tot$`L_CA2CA3/L_CA1`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100
mean((node_tot$`R_subiculum/R_CA1` + node_tot$`L_subiculum/L_CA1`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100
mean((node_tot$`R_ERC/R_CA1` + node_tot$`L_ERC/L_CA1`)/2, na.rm = T)/mean(node_tot$total, na.rm = T)*100


```


# individual proportions
```{r}
path_ratios <-
  data_stream %>%
  mutate(tsp_ratio = `CA2CA3/CA4DG`/`CA2CA3/CA1`,
         msp_ratio = `CA2CA3/CA1`/`ERC/CA1`)
  # mutate(tsp_ratio = `CA2CA3/CA4DG_prop`/`CA2CA3/CA1_prop`,
  #        msp_ratio = `CA2CA3/CA1_prop`/`ERC/CA1_prop`)


# ggplot(filter(path_ratios, msp_ratio <5), aes(x="variable", y=msp_ratio))+ #, fill=variable)) +
ggplot(path_ratios, aes(x="variable", y=msp_ratio))+ #, fill=variable)) +
      # geom_boxplot(aes(y = tsp_ratio),
      #              # outliers = T,
      #              outlier.shape = NA) +
  #ylim(0,5) +
   ggdist::stat_halfeye(
    ## custom bandwidth
    adjust = .5,
    ## adjust height
    width = .6,
    ## move geom to the right
    justification = -.4,
    ## remove slab interval
    .width = 0,
    point_colour = NA
    # outlier.shape = NA
    #alpha = 0.8,
   # limits = c(10, NA)
    #align = ggdist::align_boundary(at = 10)
   ) +
  geom_boxplot(width = .20,
                   #outlier.shape=8,
                   #outlier.shape = NA,
               #alpha = 0.8,
                   #notch=TRUE,
                   aes(y = msp_ratio))
  # geom_violin(aes(y = tsp_ratio))

```


# mean whole hipp
```{r}
mean(data_stream$total, na.rm = T)
sd(data_stream$total, na.rm = T)

data_stream$total %>% max(na.rm = TRUE)
data_stream$total %>% min(na.rm = TRUE)

# Coefficient of Variation.
# sd/mean
(sd(data_stream$total, na.rm = T))/(mean(data_stream$total, na.rm = T))*100

516/2665*100

```


## HERE 
















# Streamlines in TSP - CA4/DG, CA2/CA3 and CA1
# CA4DG
```{r}

node_tot <- data_stream[,which(grepl("DG", colnames(data_stream)))]

node_tot <- stream_tot[which(grepl("DG", stream_tot$Var1) | grepl("DG", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100

```













# Read in data
```{r}

# clear environment
rm(list = ls())

modality <- c("stream") #, "FA", "AD", "RD", "MD")
headers <- read.table("../../labels/subfield_MTL_labels.txt", header=T, sep="")

for (m in modality){
  temp <- list.files(path=paste0("../../data/connectomes/MTL_hipp_",m), pattern="*.csv", recursive = T, full.names = T)
  for (k in 1:length(temp)) assign(temp[k], read.csv(temp[k], header=F, sep=","))

  temp_data <- list()
  for (i in 1:length(temp)){
    temp_data[[i]] <- mget(temp[i])
    names(temp_data[[i]]) <- temp[i]
  }
  assign(paste0(m,"_data"), temp_data)
}

```


# Get connectome labels
```{r}

# Subjects in a list
sbj_list <- as.list(grep("stream", stream_data))

columns <- c()
for (i in 1:length(headers$Clear.Label)){
  for (t in 1:length(headers$Clear.Label)){
    column_name <- paste(headers$Clear.Label[i], headers$Clear.Label[t], sep="/")
    columns <- append(columns, column_name)
  }
}

```


# Normalize streamline data
```{r}
# stream_mat <- vector()
# for (i in 1:length(stream_data)){
#   stream_mat <- rbind(stream_mat, t(as.vector(
#     as.matrix(stream_data[[i]][[1]])/sum(as.matrix(stream_data[[i]][[1]])))))
# }
```

# Separate Right and Left hemisphere
```{r}

right_coor <- grep("R_", headers$Clear.Label)
left_coor <- grep("L_", headers$Clear.Label)

# Separate R and L labels
R_columns <- c()
for (i in right_coor) {
  for (t in right_coor){
    R_column_name <- paste(headers$Clear.Label[i], headers$Clear.Label[t], sep="/")
    R_columns <- append(R_columns, R_column_name)
  }
}

L_columns <- c()
for (j in left_coor){
  for (k in left_coor){
    L_column_name <- paste(headers$Clear.Label[j], headers$Clear.Label[k], sep="/")
    L_columns <- append(L_columns, L_column_name)
  }
}

```


# Averaga data for heatmaps
```{r}
for (m in modality){
  R_temp_mat <- matrix(unlist(get(paste0(m,"_data"))[[1]]),
                       ncol = length(headers$Clear.Label),
                       nrow = length(headers$Clear.Label),
                       byrow = F)[right_coor, right_coor]
  for (i in 2:length(get(paste0(m,"_data")))){
    R_temp_mat <- R_temp_mat + matrix(unlist(get(paste0(m,"_data"))[[i]]),
                                      ncol = length(headers$Clear.Label),
                                      nrow = length(headers$Clear.Label),
                                      byrow = F)[right_coor, right_coor]
  }
  R_temp_sum <- R_temp_mat/length(get(paste0(m,"_data")))
  assign(paste0("R_", m,"_sum"), R_temp_sum)
}

for (m in modality){
  L_temp_mat <- matrix(unlist(get(paste0(m,"_data"))[[1]]),
                       ncol = length(headers$Clear.Label),
                       nrow = length(headers$Clear.Label),
                       byrow = F)[left_coor, left_coor]
  for (i in 2:length(get(paste0(m,"_data")))){
    L_temp_mat <- L_temp_mat + matrix(unlist(get(paste0(m,"_data"))[[i]]),
                                      ncol = length(headers$Clear.Label),
                                      nrow = length(headers$Clear.Label),
                                      byrow = F)[left_coor, left_coor]
  }
  L_temp_sum <- L_temp_mat/length(get(paste0(m,"_data")))
  assign(paste0("L_", m,"_sum"), L_temp_sum)
}

# save(R_stream_sum, L_stream_sum,
#      R_FA_sum, L_FA_sum,
#      R_MD_sum, L_MD_sum,
#      R_AD_sum, L_AD_sum,
#      R_RD_sum, L_RD_sum,
#      file = "../output/Rdata/00_import_data_hipp+MTL_sums.RDATA")

```

# Get ready for heatmaps
```{r}
# Rearrange matrices
arran_func <- function(data){
  diag(data) <- 0
  data[lower.tri(data)] <- t(data)[lower.tri(data)]
  return(data)
}
for (m in modality){
  assign(paste0("R_", m, "_sym"), arran_func(get(paste0("R_", m, "_sum"))))
  assign(paste0("L_", m, "_sym"), arran_func(get(paste0("L_", m, "_sum"))))
}

# Melt data
for (m in modality){
  assign(paste0("R_", m, "_melt"), melt(get(paste0("R_", m, "_sym"))))
  assign(paste0("L_", m, "_melt"), melt(get(paste0("L_", m, "_sym"))))
}

# Name labels in melted data
# Right
for (m in modality){
  temp_data <- get(paste0("R_", m, "_melt"))
  for (i in 1:length(headers$Clear.Label[right_coor])){
    temp_data[,1][which(temp_data[,1] == i)] <-
      headers$Clear.Label[right_coor][i]
    temp_data[,2][which(temp_data[,2] == i)] <-
      headers$Clear.Label[right_coor][i]
  }
  temp_data[,1] <- as.factor(temp_data[,1])
  temp_data[,2] <- as.factor(temp_data[,2])
  assign(paste0("R_", m, "_clean"), temp_data)
}

# Left
for (m in modality){
  temp_data <- get(paste0("L_", m, "_melt"))
  for (i in 1:length(headers$Clear.Label[left_coor])){
    temp_data[,1][which(temp_data[,1] == i)] <-
      headers$Clear.Label[left_coor][i]
    temp_data[,2][which(temp_data[,2] == i)] <-
      headers$Clear.Label[left_coor][i]
  }
  temp_data[,1] <- as.factor(temp_data[,1])
  temp_data[,2] <- as.factor(temp_data[,2])
  assign(paste0("L_", m, "_clean"), temp_data)
}

# save(R_stream_clean, L_stream_clean,
#      # R_FA_clean, L_FA_clean,
#      # R_MD_clean, L_MD_clean,
#      # R_AD_clean, L_AD_clean,
#      # R_RD_clean, L_RD_clean,
#      file = "../output/Rdata/00_import_data_hipp+MTL_for_networks.RDATA")

# Make 0 entries NA
for (m in modality){
  # get(paste0("L_", m, "_clean"))[get(paste0("L_", m, "_clean"))$value == 0,]$value <- NA
  Ltemp_data <- get(paste0("L_", m, "_clean"))
  Ltemp_data[Ltemp_data$value == 0,]$value <- NA
  assign(paste0("L_", m, "_ready"), Ltemp_data)
  
  Rtemp_data <- get(paste0("R_", m, "_clean"))
  Rtemp_data[Rtemp_data$value == 0,]$value <- NA
  assign(paste0("R_", m, "_ready"), Rtemp_data)
}
  
```

# get rid of PRC PHC
```{r}
R_stream_heat <-
  R_stream_ready[-which(grepl("PRC", R_stream_ready$Var1) |
                 grepl("PRC", R_stream_ready$Var2) |
                 grepl("PHC", R_stream_ready$Var1) |
                 grepl("PHC", R_stream_ready$Var2) |
                 grepl("stratum", R_stream_ready$Var1) |
                 grepl("stratum", R_stream_ready$Var2)),]

L_stream_heat <-
  L_stream_ready[-which(grepl("PRC", L_stream_ready$Var1) |
                 grepl("PRC", L_stream_ready$Var2) |
                 grepl("PHC", L_stream_ready$Var1) |
                 grepl("PHC", L_stream_ready$Var2) |
                 grepl("stratum", L_stream_ready$Var1) |
                 grepl("stratum", L_stream_ready$Var2)),]
```

# Heatmaps
```{r}
# cols <- brewer.pal(5, 'Reds') #OrRd
# 
# # Clean up the names
# # RIGHT
# R_stream_heat$Var1 <-
#   gsub('R_subiculum', 'SUB',
#        gsub("R_CA1", "CA1",
#             gsub("R_CA4DG", "CA4DG",
#                  gsub("R_CA2CA3", "CA2CA3",
#                       gsub("R_ERC", "ERC", R_stream_heat$Var1)))))
# R_stream_heat$Var2 <-
#   gsub('R_subiculum', 'SUB',
#        gsub("R_CA1", "CA1",
#             gsub("R_CA4DG", "CA4DG",
#                  gsub("R_CA2CA3", "CA2CA3",
#                       gsub("R_ERC", "ERC", R_stream_heat$Var2)))))
# 
# R_stream_heat$Var1 <-
# factor(R_stream_heat$Var1,
#        levels=(c("CA4DG", "CA2CA3", "CA1", "SUB", "ERC"))) #[order(R_stream_heat$Var2)]
# 
# R_stream_heat$Var2 <-
# factor(R_stream_heat$Var2,
#        levels=(c("CA4DG", "CA2CA3", "CA1", "SUB", "ERC"))) #[order(R_stream_heat$Var2)]
# 
# # LEFT
# L_stream_heat$Var1 <-
#   gsub('L_subiculum', 'SUB',
#        gsub("L_CA1", "CA1",
#             gsub("L_CA4DG", "CA4DG",
#                  gsub("L_CA2CA3", "CA2CA3",
#                       gsub("L_ERC", "ERC", L_stream_heat$Var1)))))
# L_stream_heat$Var2 <-
#   gsub('L_subiculum', 'SUB',
#        gsub("L_CA1", "CA1",
#             gsub("L_CA4DG", "CA4DG",
#                  gsub("L_CA2CA3", "CA2CA3",
#                       gsub("L_ERC", "ERC", L_stream_heat$Var2)))))
# 
# L_stream_heat$Var1 <-
# factor(L_stream_heat$Var1,
#        levels=(c("CA4DG", "CA2CA3", "CA1", "SUB", "ERC"))) #[order(L_stream_heat$Var2)]
# 
# L_stream_heat$Var2 <-
# factor(L_stream_heat$Var2,
#        levels=(c("CA4DG", "CA2CA3", "CA1", "SUB", "ERC"))) #[order(L_stream_heat$Var2)]
# 
# 
# #for (m in modality){
# Rplot <- ggplot(get(paste0("R_", "stream", "_heat")) , aes(Var2, Var1, fill = value))+
#   geom_tile(color = "white")+
#   xlab(" ")+
#   ylab(" ")+
#   ggtitle("Right Hemisphere")+
#   scale_fill_gradientn(colours = cols,
#                        na.value = "gray20")+
#   theme(axis.text.x = element_text(angle = 90, size=12,color="black"),
#         legend.position="none",
#         legend.title = element_text(colour="black", size = 12, face = "bold"),
#         axis.text.y=element_text(size=12,color="black"),
#         axis.line.y.left =element_line(size=0.5, color = "black"),
#         axis.line.x.bottom =element_line(size=0.5, color = "black"),
#         axis.title.x = element_text(color="black", size=13, face="bold", vjust=-0.8), # vjust=0.5),
#         axis.title.y = element_text(color="black", size=13, face="bold", vjust=1.5),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_rect(fill = "transparent", color = NA),
#         plot.background = element_rect(fill = "transparent", color = NA)# vjust=0.5)
#       )
# 
# Lplot <- ggplot(get(paste0("L_", "stream", "_heat")) , aes(Var2, Var1, fill = value))+
#   geom_tile(color = "white")+
#   xlab(" ")+
#   ylab(" ")+
#   ggtitle("Left Hemisphere")+
#   scale_fill_gradientn(colours = cols,
#                        na.value = "gray20")+
#   theme(axis.text.x = element_text(angle = 90, size=12,color="black"),
#         legend.position="none",
#         legend.title = element_text(colour="black", size = 12, face = "bold"),
#         axis.text.y=element_text(size=12,color="black"),
#         axis.line.y.left =element_line(size=0.5, color = "black"),
#         axis.line.x.bottom =element_line(size=0.5, color = "black"),
#         axis.title.x = element_text(color="black", size=13, face="bold", vjust=-0.8), # vjust=0.5),
#         axis.title.y = element_text(color="black", size=13, face="bold", vjust=1.5),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_rect(fill = "transparent", color = NA),
#         plot.background = element_rect(fill = "transparent", color = NA)# vjust=0.5)
#       )
# 
# plt_legend <- get_legend(ggplot(get(paste0("R_", "stream", "_heat")) , aes(Var2, Var1, fill = value))+
#                         geom_tile()+
#                         scale_fill_gradientn(colours = cols,
#                                              name = "Streamline \ndensity"))
# 
# grid.arrange(Rplot, Lplot, plt_legend, nrow = 2, ncol = 3,
#              layout_matrix = rbind(c(1, 1, 1, 1, 2, 2, 2, 2, 3))
#              ) %>%
#  ggsave(file=paste0("../../output/plots/heatmaps/subfield_ERC_heatmaps_", "stream", ".png"),
#         width = 8, height = 3.5,
#         dpi = 300,
#         bg = "transparent",
#         device = "png")
```


# Get the total streamline densities
```{r}
stream_tot <- merge(L_stream_heat, R_stream_heat, by = c("Var1", "Var2"))
stream_tot <-
  stream_tot %>%
  mutate(tot = (value.x + value.y)/2)
stream_tot <-
  stream_tot %>%
  mutate(prop = round((stream_tot$tot/3200)*100*2))

```

# Get the total streamline densities
```{r}

stream_tot <- merge(L_stream_heat, R_stream_heat, by = c("Var1", "Var2"))
stream_tot <-
  stream_tot %>%
  mutate(tot = (value.x + value.y))

tot <- (sum(stream_tot$value.x, na.rm = TRUE) + sum(stream_tot$value.y, na.rm = TRUE))/2
stream_tot$prop <- stream_tot$tot/tot*100

```

# Streamlines in TSP - CA4/DG, CA2/CA3 and CA1
# CA4DG
```{r}
node_tot <- stream_tot[which(grepl("DG", stream_tot$Var1) | grepl("DG", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100
node_tot
```

# CA2CA3
```{r}
node_tot <- stream_tot[which(grepl("CA2CA3", stream_tot$Var1) | grepl("CA2CA3", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100

```

# CA1
```{r}
node_tot <- stream_tot[which(grepl("CA1", stream_tot$Var1) | grepl("CA1", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100

```

# MSP 
```{r}
node_tot <- stream_tot[which(grepl("ERC", stream_tot$Var1) | grepl("ERC", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100

```

# No SUB
```{r}
node_tot <- stream_tot[-which(grepl("SUB", stream_tot$Var1) | grepl("SUB", stream_tot$Var2)),]
node_tot$tot <- node_tot$value.x + node_tot$value.y
temp_tot <- (sum(node_tot$value.x, na.rm = TRUE) + sum(node_tot$value.y, na.rm = TRUE))/2
node_tot$prop <- node_tot$tot/temp_tot*100

```


```{r}


```



# END #